\documentclass{article}%
\usepackage[T1]{fontenc}%
\usepackage[utf8]{inputenc}%
\usepackage{lmodern}%
\usepackage{textcomp}%
\usepackage{lastpage}%
\usepackage{parskip}%
\usepackage{geometry}%
\geometry{margin=.07in}%
\usepackage{fdsymbol}%
%
%
%
\begin{document}%
\normalsize%
\newcommand{\card}[3]{\fbox{\begin{minipage}[t][#1][t]{#2} #3 \end{minipage}}}%
\card{89mm}{64mm}{\textbf{\large{Void}} 
 
\emph{Target:} Self 
 
\smallskip  \hrule \smallskip Next time you or your weapon would be affected by an invocation, negate it. 
 
}%
\card{89mm}{64mm}{\textbf{\large{Flinch}} 
 
\emph{Target:} Self 
 
\smallskip  \hrule \smallskip Next time you would take 7 or more damage, gain magical armor (-7 (B), -7 (P), -7 (S)), only for that attack. 
 
}%
\card{89mm}{64mm}{\textbf{\large{Bolster}} 
 
\emph{Target:} Self 
 
\smallskip  \hrule \smallskip Raise CON by 1 for an hour. 
 
}%
\newline%
\card{89mm}{64mm}{\textbf{\large{Strain}} 
 
\emph{Target:} Self 
 
\smallskip  \hrule \smallskip Raise STR by 1 for an hour. 
 
}%
\card{89mm}{64mm}{\textbf{\large{Grace}} 
 
\emph{Target:} Self 
 
\smallskip  \hrule \smallskip Raise AGI by 1 for an hour. 
 
}%
\card{89mm}{64mm}{\textbf{\large{Leap}} 
 
\emph{Target:} Self 
 
\smallskip  \hrule \smallskip Jump 30 feet, ignore 30 feet of fall damage 
 
}%
\newline%
\card{89mm}{64mm}{\textbf{\large{Valiikon's Blessing}} 
 
\emph{Target:} Self 
 
\smallskip  \hrule \smallskip (1n1) to consume. For 6 rounds, any poison damage you take heals you. 
 
\smallskip  \hrule \smallskip \textit{A perpetually green and dewy strip of leaf. Wearing it engenders a sense of peace.} 
 
}%
\card{89mm}{64mm}{\textbf{\large{Invocation of Harm}} 
 
\emph{Target:} Weapon 
 
\smallskip  \hrule \smallskip Roll max damage for one die (up to 6 damage). Consumed on hit. 
 
}%
\card{89mm}{64mm}{\textbf{\large{Folly of the Strong}} 
 
\emph{Target:} Weapon 
 
\smallskip  \hrule \smallskip Activates on parrying a blow from a weapon. That weapon becomes much heavier. The weapon's STR requirement goes up by 2 for 1 hour. 
 
}%
\newline%
\newpage%
\card{89mm}{64mm}{\textbf{\large{Cunning}} 
 
\emph{Target:} Weapon 
 
\smallskip  \hrule \smallskip If you parry a weapon that has an invocation, break this invocation, this invocation becomes what that one was. 
 
}%
\card{89mm}{64mm}{\textbf{\large{Blunder}} 
 
\emph{Target:} Weapon 
 
\smallskip  \hrule \smallskip On attack take 2d6 damage, DC 12 DEX check or drop your weapon. 
 
}%
\card{89mm}{64mm}{\textbf{\large{Greater Deft and Dreaming}} 
 
\emph{Target:} Weapon 
 
\smallskip  \hrule \smallskip While applied to a weapon, the weapon is invisible and the weapon passes through objects and walls. On attack, ignore all armor. When attacking with this invocation, lower enemy dodge by 4. Consumed on hit. 
 
\smallskip  \hrule \smallskip \textit{Free floating edges and inscriptions dancing with reflections from unseen light. The ribbon of runes is entirely weightless and nearly invisible.} 
 
}%
\newline%
\card{89mm}{64mm}{\textbf{\large{Lesser Deft and Dreaming}} 
 
\emph{Target:} Weapon 
 
\smallskip  \hrule \smallskip While applied to a weapon and held, the weapon passes through non-organic material. On attack, ignore non-natural armor. Consumed on hit. 
 
\smallskip  \hrule \smallskip \textit{A smooth silvery strip of fabric, the edges and inscriptions dance with reflections from unseen light. The ribbon of runes is entirely weightless.} 
 
}%
\card{89mm}{64mm}{\textbf{\large{True Edge}} 
 
\emph{Target:} Weapon 
 
\smallskip  \hrule \smallskip While applied to a weapon, if the weapon would lose [bladed], break this invocation instead. 
 
}%
\card{89mm}{64mm}{\textbf{\large{The Braggart}} 
 
\smallskip  \hrule \smallskip A cloak with bright silver stitching.  When worn, DC 9 illusion of a full set of plate armor. 
 
}%
\newline%
\card{89mm}{64mm}{\textbf{\large{Lost}} 
 
\smallskip  \hrule \smallskip Two stone birds that constantly tug towards each other, regardless of distance. 
 
}%
\card{89mm}{64mm}{\textbf{\large{Bandage}} 
 
\smallskip  \hrule \smallskip Spend (3n1). Remove 1 bleed. Bandages can be improvised out of any cloth. 
 
\smallskip  \hrule \smallskip \textit{A roll of clean cloth.} 
 
}%
\card{89mm}{64mm}{\textbf{\large{Simple Whetstone}} 
 
\smallskip  \hrule \smallskip Apply [sharpened] to a [bladed] weapon, takes 30 minutes to apply. The weapon does +1 damage and ignores 1 armor. [sharpened] is lost when you roll a 1 with a damage die. 
 
\smallskip  \hrule \smallskip \textit{A large flat stone bearing faded inscriptions.} 
 
}%
\newline%
\newpage%
\card{89mm}{64mm}{\textbf{\large{Troll Salts}} 
 
\smallskip  \hrule \smallskip Remove 1 [exhaustion], after 10 minutes take 2 [exhaustion]. Wake up from unconsciousness not caused by negative health. 
 
\smallskip  \hrule \smallskip \textit{A small earthenware jar filled with a strong-smelling coarse powder, sealed with a waxed ball of plant fiber.} 
 
}%
\card{89mm}{64mm}{\textbf{\large{Stolen Ichor}} 
 
\smallskip  \hrule \smallskip (2n1). Get 4 heal. 
 
}%
\card{89mm}{64mm}{\textbf{\large{Variigoshlovr Root }} 
 
\smallskip  \hrule \smallskip (1n1). Remove 1 bleed. 
 
}%
\newline%
\card{89mm}{64mm}{\textbf{\large{Glowing Root Bundle}} 
 
\smallskip  \hrule \smallskip (1n1). Instantly gain 4 HP. 
 
}%
\card{89mm}{64mm}{\textbf{\large{Valiikon's Whetstone}} 
 
\smallskip  \hrule \smallskip Takes 30 minutes to apply [sharpened]. Inflict 1 poison on hit. Inflict 1 poison if you do 2 poison in one turn. Rolling minimum damage removes [sharpened]. 
 
}%
\card{89mm}{64mm}{\textbf{\large{Vial of Verdant Sap}} 
 
\smallskip  \hrule \smallskip (2n1). Gain 2 heal. 
 
}%
\newline%
\card{89mm}{64mm}{\textbf{\large{Footsoldier's Whetstone}} 
 
\smallskip  \hrule \smallskip Takes 30 minutes to apply [sharpened] to a [bladed] weapon. Ignore 3 armor. Rolling 1 for damage twice removes [sharpened]. 
 
\smallskip  \hrule \smallskip \textit{A fragment of a relief etched into heavy white stone. The relief depicts a phalanx of soldiers in formation bearing partisans against an unseen force. The relief is etched deeply with identical runes in various styles.} 
 
}%
\card{89mm}{64mm}{\textbf{\large{Cannibal Whetstone}} 
 
\smallskip  \hrule \smallskip Takes 2 hours to apply [sharpened] to a [bladed] weapon. Whetstone must be soaked in blood before use. Inflict 1 [bleed] on hit. Gain 1 HP at the beginning of your turn as long as the opponent is bleeding. 
 
\smallskip  \hrule \smallskip \textit{A warm mass of striated stone writhing almost imperceptibly. It bears a closed eye on one side, it emanates a silent screaming call.} 
 
}%
\card{89mm}{64mm}{\textbf{\large{Crude Frog Idol}} 
 
\smallskip  \hrule \smallskip (3n1). Must be holding the idol with both hands. Ignore 3 poison damage next turn. 
 
\smallskip  \hrule \smallskip \textit{A small, worn, and stained frog idol on a fraying cord of twine. It's wearing an even smaller straw hat. He seems to be smiling.} 
 
}%
\newline%
\newpage%
\card{89mm}{64mm}{\textbf{\large{Battle Egg Carton and Bandolier}} 
 
\smallskip  \hrule \smallskip Carton holds 24 Putrefying Eggs. Carton will break if it or the person wearing it takes 12 damage in one turn. 
 
\smallskip  \hrule \smallskip \textit{A wooden case made from solid hardwood with round impressions chipped into it. The inside is padded with soft moss.} 
 
}%
\card{89mm}{64mm}{\textbf{\large{Bag of Salt}} 
 
\smallskip  \hrule \smallskip Worth 1d12*10f. 
 
}%
\card{89mm}{64mm}{\textbf{\large{Salorbrious}} 
 
\smallskip  \hrule \smallskip For 6 turns, gain 1 SALT every turn. 
 
\smallskip  \hrule \smallskip \textit{A smooth waxed sphere of pure SALT, it feels heavy in the hand. It's just enough to kill a man.} 
 
}%
\newline%
\card{89mm}{64mm}{\textbf{\large{Tall Salted Peter}} 
 
\smallskip  \hrule \smallskip Gain 3 SALT. 
 
\smallskip  \hrule \smallskip \textit{A long clay vial filled with salt suspended in a dark brown oil and continuously swirling and glittering .} 
 
}%
\card{89mm}{64mm}{\textbf{\large{Curse Eye}} 
 
\smallskip  \hrule \smallskip When crushed, all characters within 3 spaces gain 1d4 CURSE. 
 
\smallskip  \hrule \smallskip \textit{A brittle dull black sphere with a layer of veins on one side.} 
 
}%
\card{89mm}{64mm}{\textbf{\large{Rucksack}} 
 
\smallskip  \hrule \smallskip Max encumbrance: 6 + STR, [encumbered] threshold: 3 + STR. 
 
}%
\newline%
\card{89mm}{64mm}{\textbf{\large{Sling Bag}} 
 
\smallskip  \hrule \smallskip Can be worn with another bag. Max encumbrance: 3. This bag can be switched from being worn on your front or back for [1n1]. Searching and grabbing something from this bag is [2n1]. 
 
}%
\card{89mm}{64mm}{\textbf{\large{Scout's Bag}} 
 
\smallskip  \hrule \smallskip Max encumbrance: 4 + STR. 
 
}%
\card{89mm}{64mm}{\textbf{\large{Frame Bag}} 
 
\smallskip  \hrule \smallskip Max encumbrance: 8+STR. [enumbered] threshold: 2+STR. 
 
}%
\newline%
\newpage%
\card{89mm}{64mm}{\textbf{\large{Stick Bag}} 
 
\smallskip  \hrule \smallskip Can be carried while wearing another bag. Stick must be held with one hand. Max encumbrance: 2 + STR. 
 
}%
\card{89mm}{64mm}{\textbf{\large{Salt Wretch}} 
 
\emph{HP:} 1d10 or 4 
 
\emph{Scores:} 1 STR 
 
\emph{Skills:} - Claw (2n1): 1d4 (S). Enemies take damage = to their current SALT on the beginning of their turn and lose one SALT when within 1 space of the Wretch. 
 
\emph{Holds:} 1d4-3 pickaxe, 1d4-2 curse\_eye. 
 
\smallskip  \hrule \smallskip \textit{A bent creature, shriviled and distended. Rattling sandpaper breathing and muttering. Eyes shriveled and wasted, or a dull black.} 
 
}%
\card{89mm}{64mm}{\textbf{\large{Crust Punk}} 
 
\emph{HP:} 4d10 or 20 
 
\emph{Scores:} 2 STR, 1 CON, 2 HYLIC 
 
\emph{Holds:} 2d100f of SALT. 
 
}%
\newline%
\card{89mm}{64mm}{\textbf{\large{Nightlight Chicken}} 
 
\emph{HP:} 1d6 or 3 
 
\emph{Scores:} -1 STR, 1 AGI  
 
\emph{Skills:} - Peck and Scratch, (3n1): 1d4-1 (S) + 1 (P).  
 
}%
\card{89mm}{64mm}{\textbf{\large{Starving Harvester}} 
 
\emph{HP:} 2d12 13 
 
\emph{Scores:} 1 STR, 1 AGI, 1 CON, 1 HYLIC 
 
\emph{Holds:} foul\_club, hunting\_knife are both standard. Otherwise, really any sharp knife and any bludgeoning weapon, as likely improvised. Weaker Harvesters will tend to have worse equipment. 1d100f of SALT. 
 
}%
\card{89mm}{64mm}{\textbf{\large{Gluttonous Harvester}} 
 
\emph{HP:} 3d12 19 
 
\emph{Scores:} 2 STR, 2 AGI, 2 CON, 2 HYLIC 
 
\emph{Holds:} crimson\_cudgel, cruel\_razor, potentially foul\_club or hunting\_knife. 2d100f of SALT. 
 
}%
\newline%
\card{89mm}{64mm}{\textbf{\large{Feasting Harvester}} 
 
\emph{HP:} 5d12 or 32 
 
\emph{Scores:} 2 STR, 2 AGI, 3 CON, 4 HYLIC 
 
\emph{Holds:} weeping\_greatclub, screeching\_sickle, are unique to powerful Harvesters. Harvesters might also use other fine bludgeoning weapons or sharp knives. 1d4-1 hunting\_net. 4d100f of SALT. 
 
}%
\card{89mm}{64mm}{\textbf{\large{Gold Eater}} 
 
\emph{HP:} 5d6 or 18 
 
\emph{Scores:} 1d4-1 or 2 STR, -2 AGI and DEX, 0 PERCEPTION 
 
}%
\card{89mm}{64mm}{\textbf{\large{Ibex Duke}} 
 
\emph{HP:} 1d12 or 6  
 
\emph{Scores:} 1 STR, 1 AGI 
 
}%
\newline%
\newpage%
\card{89mm}{64mm}{\textbf{\large{Ibex King}} 
 
\emph{HP:} 3d12 or 19 
 
\emph{Scores:} 1 STR, 1 AGI 
 
}%
\card{89mm}{64mm}{\textbf{\large{Illuminated Wretch}} 
 
\emph{HP:} 1d8 or 4 
 
\emph{Scores:} -1 all core stats, 1 PSYCHIC 
 
}%
\card{89mm}{64mm}{\textbf{\large{Lionhead}} 
 
\emph{HP:} 1d12 or 6 
 
\emph{Scores:} -1 all core stats, 3 PSYCHIC 
 
}%
\newline%
\card{89mm}{64mm}{\textbf{\large{Ant Scout}} 
 
\emph{HP:} 1d12 or 6 
 
\emph{Scores:} 1 STEALTH 
 
}%
\card{89mm}{64mm}{\textbf{\large{Ant Soldier}} 
 
\emph{HP:} 3d10 or 16 
 
\emph{Scores:} 1 STR, 1 AGI, 1 DEX  
 
}%
\card{89mm}{64mm}{\textbf{\large{Ant Demon}} 
 
\emph{HP:} 5d10 or 27 
 
\emph{Scores:} 3 STR, 2 AGI 
 
}%
\newline%
\card{89mm}{64mm}{\textbf{\large{Tchok}} 
 
\emph{HP:} 3d8+1 or 13 
 
\emph{Scores:} 1 CON 
 
\emph{Skills:} - Jibbering (1n1) All checks related to magic made within earshot of a jibbering Tchok are made with -3. This effect stacks with multiple instances of jibbering. 
 
\emph{Holds:} Carrying 1d4 daggers, 1d6 short spears. 1d6 clubs. 1d2 blowguns.
More rarely poisons that push back the furthest AP token by 1 slot on hit, consumed on hit. Even more rarely, daggers that can deliver 3 doses of poison before reapplication is necessary.
 
 
\smallskip  \hrule \smallskip \textit{Slimy, stupid, and inane.} 
 
}%
\card{89mm}{64mm}{\textbf{\large{Charge}} 
 
\emph{Requirements:} 1 STR 
 
\smallskip  \hrule \smallskip Charge is (1n1). Move double your movement speed in a straight line, must move at least two hexes.  Once you reach an enemy, you may perform an attack. If your attack hits you can choose to add your STR to the damage. If you are entering a STR contest of some kind, add your STR to your roll again. 
 
\emph{Cost:} 1 SP 
 
}%
\card{89mm}{64mm}{\textbf{\large{Crush}} 
 
\emph{Requirements:} 2 STR, a [swinging] (B) attack that uses +STR to-hit 
 
\smallskip  \hrule \smallskip Spend an extra 1 AP. If crush hits, use the attack roll as a check against the enemies STR. If the attacking roll is higher, the defender is knocked prone and [vulnerable]. 
 
\emph{Cost:} 1 SP 
 
}%
\newline%
\newpage%
\card{89mm}{64mm}{\textbf{\large{Quick to Act}} 
 
\emph{Requirements:} 1 AGI 
 
\smallskip  \hrule \smallskip Raise your initiative by 3. 
 
\emph{Cost:} 1 SP 
 
}%
\card{89mm}{64mm}{\textbf{\large{Mobility}} 
 
\emph{Requirements:} 1 AGI 
 
\smallskip  \hrule \smallskip Every turn, you can move 1 space for free (as long as you can currently move). 
 
\emph{Cost:} 1 SP 
 
}%
\card{89mm}{64mm}{\textbf{\large{Parry}} 
 
\emph{Requirements:} 1 AGI, a [finesse] weapon or shield.  
 
\smallskip  \hrule \smallskip Parry can be used to attempt to [interrupt] a melee attack. Pay (2n1). Contest the attack roll with a Parry attempt, a check + AGI or DEX. If you win, the attack does no damage and you gain 2 Temp AP. 
 
\emph{Cost:} 1 SP 
 
}%
\newline%
\card{89mm}{64mm}{\textbf{\large{Evasive}} 
 
\emph{Requirements:} Requires: 2 AGI, a [finesse] weapon or shield.   
 
\smallskip  \hrule \smallskip Add 2 to your to-hit difficulty for every [finesse] weapon or [finesse] shield you are wielding, up to 4. 
 
\emph{Cost:} 1 SP 
 
}%
\card{89mm}{64mm}{\textbf{\large{Feint}} 
 
\emph{Requirements:} 1 AGI 
 
\smallskip  \hrule \smallskip (1n2). Roll a check +AGI against your enemies passive AGI or PERCEPTION, whichever is higher. If you win, you can perform 1 action without triggering [interrupt]s from that enemy. The enemy is considered [vulnerable] until your (or your allies') next action. 
 
\emph{Cost:} 1 SP 
 
}%
\card{89mm}{64mm}{\textbf{\large{Pulling Punches}} 
 
\emph{Requirements:} 1 DEX 
 
\smallskip  \hrule \smallskip When you roll damage dice for an attack, you can choose to set a max damage, (example: treat any number above a 4 as a 4). You can also choose to do non-lethal damage if the damage type is (B). 
 
\emph{Cost:} 1 SP 
 
}%
\newline%
\card{89mm}{64mm}{\textbf{\large{Draw!}} 
 
\emph{Requirements:} 1 DEX 
 
\smallskip  \hrule \smallskip You may ignore weapon switching costs if you either switch [one-handed] weapons or draw a one handed weapon and immediately attempt an attack. 
 
\emph{Cost:} 1 SP 
 
}%
\card{89mm}{64mm}{\textbf{\large{Fast Recovery}} 
 
\emph{Requirements:} 1 CON 
 
\smallskip  \hrule \smallskip Your recovery dice are d10s rather than d6s. 
 
\emph{Cost:} 1 SP 
 
}%
\card{89mm}{64mm}{\textbf{\large{Hearty}} 
 
\emph{Requirements:} 2 CON 
 
\smallskip  \hrule \smallskip Get +6 Health. You can take this skill twice. 
 
\emph{Cost:} 1 SP 
 
}%
\newline%
\newpage%
\card{89mm}{64mm}{\textbf{\large{Precision}} 
 
\emph{Requirements:} 1 PERCEPTION 
 
\smallskip  \hrule \smallskip (1n1). You can use Precision right before any attack, including an interrupt. If the attack lands, treat one damage die (up to d8) as landing on max damage. 
 
\emph{Cost:} 1 SP 
 
}%
\card{89mm}{64mm}{\textbf{\large{Focus}} 
 
\emph{Requirements:} 1 PERCEPTION 
 
\smallskip  \hrule \smallskip (1n1). You can use Focus right before any attack, including an interrupt. Add your PERCEPTION to hit. 
 
\emph{Cost:} 1 SP 
 
}%
\card{89mm}{64mm}{\textbf{\large{Finisher}} 
 
\smallskip  \hrule \smallskip Use this before performing an attack. Lose 1 AP. If double the damage would kill the opponent, treat the attack as dealing double damage (max +10), if you kill with the move regain 1 AP. 
 
\emph{Cost:} 1 SP 
 
}%
\newline%
\card{89mm}{64mm}{\textbf{\large{Momentum}} 
 
\smallskip  \hrule \smallskip When you kill an opponent, regain 1 AP. 
 
\emph{Cost:} 1 SP 
 
}%
\card{89mm}{64mm}{\textbf{\large{Dual Wielding 1: Ambidextrous}} 
 
\emph{Requirements:} AGI 1 
 
\smallskip  \hrule \smallskip You can attack with your offhand as well as you attack with your main hand. Track the costs from their [BA]s separately, attacks with one do not affect the other. 
 
\emph{Cost:} 1 SP 
 
}%
\card{89mm}{64mm}{\textbf{\large{Dual Wielding 2: Simultaneous Attack}} 
 
\emph{Requirements:} AGI 1, STR 1, Dual Wielding 1 
 
\smallskip  \hrule \smallskip Once per turn, you can attack with both of your weapons at the same time spending 1 less AP than you would to do the attacks separately. Perform the attacks as normal otherwise. 
 
\emph{Cost:} 1 SP 
 
}%
\newline%
\card{89mm}{64mm}{\textbf{\large{Dual Wielding 3: Flurry}} 
 
\emph{Requirements:} AGI 2, STR 2, Dual Wielding 2 
 
\smallskip  \hrule \smallskip If you roll max damage with one of your weapons, you can attack again with the other spending 1 AP less than you normally would. You can use Simultaneous Attack multiple times per turn. 
 
\emph{Cost:} 1 SP 
 
}%
\card{89mm}{64mm}{\textbf{\large{Large Weapon 1: [two-handed] Proficiency}} 
 
\emph{Requirements:} 2 STR 
 
\smallskip  \hrule \smallskip Treat your Strength as 1 higher (for weapon related rolls) when wielding two handed weapons. 
 
\emph{Cost:} 1 SP 
 
}%
\card{89mm}{64mm}{\textbf{\large{Large Weapon 2: Sweep}} 
 
\emph{Requirements:} Large Weapon 1, STR 2  
 
\smallskip  \hrule \smallskip You can perform a given [swinging] melee attack to attack two adjacent enemies in one strike, or spend an extra 1 AP and attack up to four adjacent enemies (that you could hit normally) while using a [two-handed] weapon. 
 
\emph{Cost:} 1 SP 
 
}%
\newline%
\newpage%
\card{89mm}{64mm}{\textbf{\large{Large Weapon 2: Giant Weapon Proficiency}} 
 
\emph{Requirements:} Large Weapon 1 
 
\smallskip  \hrule \smallskip Treat your Strength as 1 higher (for weapon related rolls) when wielding a weapon with the [giant] tag. 
 
\emph{Cost:} 1 SP 
 
}%
\card{89mm}{64mm}{\textbf{\large{Large Weapon 2: Giant Weapon Efficiency}} 
 
\emph{Requirements:} Large Weapon 2: Giant Weapon Proficiency, AGI 2 
 
\smallskip  \hrule \smallskip When you land a hit with a [giant] weapon, gain 1 Temp AP. 
 
\emph{Cost:} 1 SP 
 
}%
\card{89mm}{64mm}{\textbf{\large{Storm Gate}} 
 
\emph{Requirements:} LIGHTNING 1  
 
\smallskip  \hrule \smallskip Spend 1 recovery die (do not heal). Immediately lose 1 max AP. At the beginning of every turn, (after AP is regained) gain 1 charge for every AP you have. This ability lasts a number of hours equal to your LIGHTNING score. Once the ability ends, regain 1 max AP. 
 
\emph{Cost:} 1 SP 
 
}%
\newline%
\card{89mm}{64mm}{\textbf{\large{Skillful Conduit}} 
 
\emph{Requirements:} LIGHTNING 1  
 
\smallskip  \hrule \smallskip You're able to transfer up to your LIGHTNING score in charges with every hit, including when using [ranged] attacks. 
 
\emph{Cost:} 1 SP 
 
}%
\card{89mm}{64mm}{\textbf{\large{Crashing Step}} 
 
\emph{Requirements:} LIGHTNING 1 
 
\smallskip  \hrule \smallskip Spend 1 charge and (1n1). Move 6 spaces, you are able to turn at any angle, but only once. You must be able to move through the space normally. You move from space to space near instantaneously, and cannot be attacked or interrupted while moving. When you arrive at your target space, you can choose to transfer 1 charge to an enemy within 2 spaces. 
 
\emph{Cost:} 1 SP 
 
}%
\card{89mm}{64mm}{\textbf{\large{Watched by Dark Clouds}} 
 
\emph{Requirements:} LIGHTNING 1 
 
\smallskip  \hrule \smallskip You must be using Storm Gate to use this ability. Spend 1 charge. You're able to keep 1 entity (including yourself) from losing charge at the end of their turn (as long as they are within your range). If you cast this on another creature, you know the direction they are in and a rough estimate of distance. If you cast it on yourself, you know the direction and the rough distance to a number of creatures equal to your LIGHTNING score. This ability ignores stealth or other concealment. This means that, for example, you could not be caught unaware in melee. This effect ends when Storm Gate does. 
 
\emph{Cost:} 1 SP 
 
}%
\newline%
\card{89mm}{64mm}{\textbf{\large{Silent Light}} 
 
\emph{Requirements:} LIGHTNING 1 
 
\smallskip  \hrule \smallskip Spend 1 extra charge when you perform a LIGHTNING magic. You can choose either to prevent light or sound from being produced. 
 
\emph{Cost:} 1 SP 
 
}%
\card{89mm}{64mm}{\textbf{\large{Fingers of Light}} 
 
\emph{Requirements:} LIGHTNING 1 
 
\smallskip  \hrule \smallskip An attack. The target must have at least 1 charge. Range: 3 spaces. Costs (1n3) and all of your charge. 
+3*LIGHTNING to hit, roll a d6 for every charge you have (P). 
 
\emph{Cost:} 1 SP 
 
}%
\card{89mm}{64mm}{\textbf{\large{Spark}} 
 
\emph{Requirements:} LIGHTNING 1 
 
\smallskip  \hrule \smallskip An attack. Range: 3 spaces. (2n1), 1d4 (P) damage. Transfer 1 charge between yourself and whoever is hit.
Call Lightning: a much bigger move, sort of a signature move for the class, lightning hits whatever has the most charge, doing tons of damage 
 
\emph{Cost:} 1 SP 
 
}%
\newline%
\newpage%
\card{89mm}{64mm}{\textbf{\large{Improvised Medicine}} 
 
\emph{Requirements:} 2 MED, 1 DEX 
 
\smallskip  \hrule \smallskip You are able to do your work under quite poor conditions. You can performing surgery with a dagger, tear the stitching out of a backpack and use it to close a wound, and quickly create makeshift bandages from a torn cloak.
Lower your effective MED by 1 to replace 1 point of medical equipment up to 3 points of medical equipment. Explain where you're getting this material and how getting that material changes the source of the material (i.e. Your patients cloak now has a strip torn out, the haft of an axe was broken in half to be used as a splint). 
 
}%
\card{89mm}{64mm}{\textbf{\large{Severe Case}} 
 
\emph{Requirements:} 2 MED, 1 DEX 
 
\smallskip  \hrule \smallskip If the character has no more recovery dice to spend but a MED skill requires spending recovery dice you can attempt to perform the MED skill anyway. Spend the resources and time required to perform the skill as usual but then make a MED check against a DC of 9. If you pass, you succeed. Otherwise, nothing happens. 
 
}%
\card{89mm}{64mm}{\textbf{\large{Emergency Care}} 
 
\emph{Requirements:} 2 MED, 1 DEX 
 
\smallskip  \hrule \smallskip This skill is to be used on someone who is downed and rolling death checks. Take (2n1), add your MED score to their death check. Consume 1 point of medical equipment. You can do this multiple times in a turn. 
 
}%
\newline%
\card{89mm}{64mm}{\textbf{\large{Tend to the Wounded}} 
 
\emph{Requirements:} 1 MED, 1 DEX 
 
\smallskip  \hrule \smallskip Tend to someone taking one hour to rest and spend 1 recovery die. They only spend the 1 recovery die, but they get to roll to gain 3 recovery dice + your MED score. Consume 3 points of medical equipment. They have to rest that full hour, but you only have to tend to them for 30 minutes. 
 
}%
\card{89mm}{64mm}{\textbf{\large{Triage}} 
 
\emph{Requirements:} 1 MED 
 
\smallskip  \hrule \smallskip Consume 1 point of medical equipment, allow a conscious character to immediately roll a recovery die. Takes 5 minutes. 
 
}%
\card{89mm}{64mm}{\textbf{\large{Dissection}} 
 
\emph{Requirements:} 1 MED 
 
\smallskip  \hrule \smallskip Dissect a human or humanoid specimen that has recently died. Takes 2 hours. Roll a MED check against a DC of 9 - the number of additional hours taken dissecting the specimen. If you succeed, gain 1 SP that must be spent on your MED score or MED skills.
This is considered desecrating a corpse my most groups. Having dissections attributed to you will tend to lower your reputation with a group. 
 
}%
\newline%
\card{89mm}{64mm}{\textbf{\large{Edge Alignment}} 
 
\emph{Requirements:} 1 AGI, 1 DEX 
 
\smallskip  \hrule \smallskip Ignore 1 extra armor when using a [bladed] weapon. The first time you would lose [sharpened] after sharpening a weapon, don't. 
 
\emph{Cost:} 1 SP 
 
}%
\card{89mm}{64mm}{\textbf{\large{Defensive Perimeter}} 
 
\emph{Requirements:} A melee weapon with [reach] and [hafted] and an attack with $\blacktriangle$, STR 1 
 
\smallskip  \hrule \smallskip (1n1). You brace the weapon, typically a spear. If an enemy moves into a space threatened by you, you get to use an attack immediately for 1 AP less than you would have to spend otherwise. If your attack does damage, Roll a STR contest. If you win, their action ends and they stop moving, stopping outside of your range. You get 1 Temp AP. You can spend it to immediately get back into “Defensive Perimeter”. 
 
\emph{Cost:} 1 SP 
 
}%
\card{89mm}{64mm}{\textbf{\large{Sharpshooter}} 
 
\emph{Requirements:} 1 PERCEPTION 
 
\smallskip  \hrule \smallskip When making [ranged] attacks, treat your PERCEPTION as 1 higher. 
 
\emph{Cost:} 1 SP 
 
}%
\newline%
\newpage%
\card{89mm}{64mm}{\textbf{\large{Trick Shot}} 
 
\emph{Requirements:} 1 PERCEPTION 
 
\smallskip  \hrule \smallskip +2 To-Hit when using "Called Shot" with a [ranged] attack. 
 
\emph{Cost:} 1 SP 
 
}%
\card{89mm}{64mm}{\textbf{\large{Shield Training}} 
 
\smallskip  \hrule \smallskip Raise your To-Hit by 2 against melee attacks and by 3 against ranged attacks when using a shield. 
 
\emph{Cost:} 1 SP 
 
}%
\card{89mm}{64mm}{\textbf{\large{Shield Bash}} 
 
\smallskip  \hrule \smallskip You can attack with a shield as +STR to hit, 1d4+STR.  
 
\emph{Cost:} 1 SP 
 
}%
\newline%
\card{89mm}{64mm}{\textbf{\large{Sneak Attack 1: Lucky Strike}} 
 
\emph{Requirements:} AGI 1, [stealth] weapon 
 
\smallskip  \hrule \smallskip Sneak attack dice are exploding (if you get the max value on a die, roll another, if it happens again, roll another, etc.). If a die is set to max, roll another die. 
 
\emph{Cost:} 1 SP 
 
}%
\card{89mm}{64mm}{\textbf{\large{Sneak Attack 2: Precision Strike}} 
 
\emph{Requirements:} 1 STEALTH , [stealth] or [finesse] weapon 
 
\smallskip  \hrule \smallskip Before you attack, you can choose to increase the cost of your attack by 1 AP to roll an extra damage die.

Max 1 damage die when you attack a [vulnerable] opponent (unaware opponents are [vulnerable]). 
 
\emph{Cost:} 1 SP 
 
}%
\card{89mm}{64mm}{\textbf{\large{Sneak Attack 2: Twist the Knife}} 
 
\emph{Requirements:} 1 STEALTH , [stealth] weapon 
 
\smallskip  \hrule \smallskip After performing an attack you can spend [1n2] to roll another damage die and add it to the attack before damage multipliers are calculated. If this attack kills, regain 1 AP. 
 
\emph{Cost:} 1 SP 
 
}%
\newline%
\card{89mm}{64mm}{\textbf{\large{Sneak Attack 3: Assassinate}} 
 
\emph{Requirements:} 2 STEALTH, 2 DEX, [stealth] weapon 
 
\smallskip  \hrule \smallskip Assassinate can only be used on an opponent who is unaware of you.

If you roll 3 dice at max damage, double your damage. If you roll 4, triple it. Ignore 8 armor on when using a Sneak Attack. 
 
\emph{Cost:} 1 SP 
 
}%
\card{89mm}{64mm}{\textbf{\large{Deception}} 
 
\emph{Requirements:} 1 SOCIAL 
 
\smallskip  \hrule \smallskip +2 to SOCIAL checks when lying. You can buy this skill twice. 
 
\emph{Cost:} 1 SP 
 
}%
\card{89mm}{64mm}{\textbf{\large{Disguise}} 
 
\emph{Requirements:} 1 SOCIAL 
 
\smallskip  \hrule \smallskip You can create disguises, within reason. Roll a check +3 to set a DC for your disguise, you can create a disguise for another person this way. When using a disguise you get +3 to SOCIAL or STEALTH rolls relevant to your use of the disguise. 
 
\emph{Cost:} 1 SP 
 
}%
\newline%
\newpage%
\card{89mm}{64mm}{\textbf{\large{Wrestling 1: Rasslin'}} 
 
\emph{Requirements:} AGI 2, STR 2 
 
\smallskip  \hrule \smallskip +2 to Grapple checks. 
 
\emph{Cost:} 1 SP 
 
}%
\card{89mm}{64mm}{\textbf{\large{Wrestling 2: Gottem}} 
 
\emph{Requirements:} AGI 2, STR 2, Wrestling 1 
 
\smallskip  \hrule \smallskip If you're successfully grappling a humanoid in your size category or lower, get +4 to subsequent grapple checks. If you're successfully grappling a non-humanoid in your size category, +2 to subsequent grapple checks. Otherwise, if you're successfully grappling, +1 to subsequent grapple checks. 
 
\emph{Cost:} 1 SP 
 
}%
\card{89mm}{64mm}{\textbf{\large{Wrestling 2: Choosin' a Snoozin'}} 
 
\emph{Requirements:} AGI 2, STR 2, Wrestling 1 
 
\smallskip  \hrule \smallskip Can only be performed on something that needs to breathe and... Has a neck. 

Spend an extra AP when entering a grapple check. If you can hold the grapple for 6 turns, the grappled creature is knocked out for 1d12 hours. 
 
\emph{Cost:} 1 SP 
 
}%
\newline%
\card{89mm}{64mm}{\textbf{\large{Chitinous Strata}} 
 
\emph{Requirements:} 1 HYLIC 
 
\smallskip  \hrule \smallskip (2n1) to start. Continuously burn 1 SALT for 1 hour. Generate a layer of salt armor with (-1d6 B, -1d8 P, -1d8 S). Lower your to-hit difficulty by 1. While using Salt Armor, you're able to use an unarmed attack of +AGI to hit, 1d4 (B) [range: close]. Disadvantage on anything requiring fine motor skills. You cannot wear other armor while using this ability. You can use this ability multiple times.

 \medskip

Flare Effect: Must currently have Salt Armor. Burn 1 Salt. Triple armor bonus from this source for 1 turn.
 
 
\emph{Cost:} 1 SP 
 
}%
\card{89mm}{64mm}{\textbf{\large{Violent Accretion}} 
 
\emph{Requirements:} 1 HYLIC 
 
\smallskip  \hrule \smallskip (1n1) to start. Continuously burn 1 SALT for 1 hour. Salt rapidly accrues on an arm, covering it in thick plates and amplifying its strength. While using Violent Accretion you have minimal use of the hand which is encased in thick plates of armor with few joints and little to no finger separation. Take disadvantage on anything requiring fine motor skills, and take disadvantage when using other weapons. When using Violent Accretion the arm functions as the following weapon:

 \medskip

[one-handed] [range: close]  
Speed: (1n1)$\Rightarrow$(2n1) To Hit: 2*STR  
- 1d8+STR (B)

 \medskip

If flared for 1 SALT, lasting for 1 attack:

 \medskip

[one-handed]
Speed: (2n1) To Hit: 2*STR
- 1d8 (B) 2d8 (P) +STR 
 
\emph{Cost:} 1 SP 
 
}%
\card{89mm}{64mm}{\textbf{\large{Salubrity}} 
 
\emph{Requirements:} 1 HYLIC 
 
\smallskip  \hrule \smallskip This ability allows you to augment scores and abilities by burning SALT. This skill will probably have to be streamlined, rewritten.
(1n1) to start all of these moves.
STR: Increase STR by 2 for 1 hour by continuously burning SALT.
CON: Increase CON by 2 for 1 hour by continuously burning SALT.
Both of these can be flared to increase by 1 more for 1 minute.  

 \medskip

If you have at least 2 HYLIC: 
AGI: Increase AGI and move speed by 1 and move for 1 hour by continuously burning SALT. Can be flared for 1 SALT to leap 6 spaces.
PERCEPTION: Increase perception by 1 for 6 hours by continuously burning SALT, can replace 4 hours of sleep. Can be flared by burning 1 SALT to add +3 to checks made with one sense for 5 minutes. 
 
\emph{Cost:} 1 SP 
 
}%
\newline%
\card{89mm}{64mm}{\textbf{\large{Giant Feasting Club}} 
 
\emph{Tags:} two-handed, giant, hilted 
 
\emph{Requirements:} 4 STR 
 
\emph{Speed:} (2n1) 
 
\emph{To-Hit:} +2*STR 
 
\smallskip  \hrule \smallskip \emph{Attacks: }
\begin{itemize}
    \item 2d4 (B) 2d4 (P) $\triangleright\mkern-7mu\triangleright\mkern-7mu\blacktriangleright$

\end{itemize} 
 
\smallskip  \hrule \smallskip Everytime you roll a 4 for damage, inflict 1 bleeding and 1 poison. Crush only requires 1 extra STR. 
 
\smallskip  \hrule \smallskip \textit{Only the handle of the dark hardwood club is visible. The rest is covered with enormous living barnacles, constantly chattering, clicking, moving, tearing at anything that comes near.} 
 
\vfill
        weapon \hfill Enc: 2 
        }%
\card{89mm}{64mm}{\textbf{\large{Cactus Greatclub}} 
 
\emph{Tags:} hilted, two-handed 
 
\emph{Requirements:} 2 STR 
 
\emph{Speed:} (2n1) 
 
\emph{To-Hit:} +2*STR 
 
\smallskip  \hrule \smallskip \emph{Attacks: }
\begin{itemize}
    \item 3d6 (B) + 3 (P) $\triangleright\mkern-7mu\triangleright\mkern-7mu\blacktriangleright$

\end{itemize} 
 
\smallskip  \hrule \smallskip If cactus greatclub takes 10 damage in one turn (or more) explodes, doing 2d6 (P) in short radius (half as effective against armor) 
 
\vfill
        weapon \hfill Enc: 2 
        }%
\card{89mm}{64mm}{\textbf{\large{The Serpent Lord's Coiled Greatsword}} 
 
\emph{Tags:} two-handed, bladed 
 
\emph{Requirements:} 2 AGI, 2 STR 
 
\emph{Speed:} (2n1) 
 
\emph{To-Hit:} +AGI +STR 
 
\smallskip  \hrule \smallskip \emph{Attacks: }
\begin{itemize}
    \item 3d6 (S) $\triangleright\mkern-7mu\triangleright\mkern-7mu\blacktriangleright$

\end{itemize} 
 
\smallskip  \hrule \smallskip On rolling 6, inflict 1 Poison. 
 
\vfill
        weapon \hfill Enc: 1 
        }%
\newline%
\newpage%
\card{89mm}{64mm}{\textbf{\large{Estoc}} 
 
\emph{Tags:} hilted, two-handed, reach 
 
\emph{Requirements:} 2 AGI 
 
\emph{Speed:} (1n2) 
 
\emph{To-Hit:} +AGI 
 
\smallskip  \hrule \smallskip \emph{Attacks: }
\begin{itemize}
    \item 2d6 + AGI (P) $\blacktriangle$

\end{itemize} 
 
\smallskip  \hrule \smallskip Ignore armor equal to piercing damage. 
 
\vfill
        weapon, basic \hfill Enc: 1 
        }%
\card{89mm}{64mm}{\textbf{\large{Boar Sword}} 
 
\emph{Tags:} hilted two-handed reach 
 
\emph{Requirements:} 2 AGI 
 
\emph{Speed:} (1n2)$\Rightarrow$(2n1) 
 
\emph{To-Hit:} +AGI 
 
\smallskip  \hrule \smallskip \emph{Attacks: }
\begin{itemize}
    \item 2d6 + AGI (P) $\blacktriangle$

\end{itemize} 
 
\smallskip  \hrule \smallskip Inflict 2 [bleed] 
 
\vfill
        weapon, basic \hfill Enc: 1 
        }%
\card{89mm}{64mm}{\textbf{\large{Shortsword}} 
 
\emph{Tags:} one-handed, hilted, bladed 
 
\emph{Speed:} (1n1)$\Rightarrow$(1n2) 
 
\emph{To-Hit:} +AGI 
 
\smallskip  \hrule \smallskip \emph{Attacks: }
\begin{itemize}
    \item 1d8 (P) $\blacktriangle$ or (S) $\triangleright\mkern-7mu\blacktriangleright\mkern-7mu\triangleright$

\end{itemize} 
 
\vfill
        weapon, basic \hfill Enc: 1 
        }%
\newline%
\card{89mm}{64mm}{\textbf{\large{Kukri}} 
 
\emph{Tags:} one-handed, hilted, bladed, reach: close, stealth 
 
\emph{Speed:} (1n1)$\Rightarrow$(1n1)$\Rightarrow$(1n2) 
 
\emph{To-Hit:} +DEX 
 
\smallskip  \hrule \smallskip \emph{Attacks: }
\begin{itemize}
    \item 1d4 (P) $\blacktriangle$ or (S) $\triangleright\mkern-7mu\triangleright\mkern-7mu\blacktriangleright$

\end{itemize} 
 
\vfill
        weapon, basic \hfill Enc: 1/3 
        }%
\card{89mm}{64mm}{\textbf{\large{Rondel}} 
 
\emph{Tags:} one-handed, hilted, bladed, reach: close, stealth 
 
\emph{Speed:} (1n1)$\Rightarrow$(1n1)$\Rightarrow$(1n2)  
 
\emph{To-Hit:} +DEX 
 
\smallskip  \hrule \smallskip \emph{Attacks: }
\begin{itemize}
    \item 1d4 + AGI (P) $\blacktriangle$

\end{itemize} 
 
\smallskip  \hrule \smallskip If doing piercing damage, ignore 5 non-shield armor 
 
\vfill
        weapon, basic \hfill Enc: 1/3 
        }%
\card{89mm}{64mm}{\textbf{\large{Dagger}} 
 
\emph{Tags:} one-handed, hilted, bladed, reach: close, stealth 
 
\emph{Speed:} (1n1) 
 
\emph{To-Hit:} +DEX 
 
\smallskip  \hrule \smallskip \emph{Attacks: }
\begin{itemize}
    \item 1d4 (P) $\blacktriangle$ or (S) $\triangleright\mkern-7mu\blacktriangleright\mkern-7mu\triangleright$

\end{itemize} 
 
\vfill
        weapon, basic \hfill Enc: 1/3 
        }%
\newline%
\card{89mm}{64mm}{\textbf{\large{Machete}} 
 
\emph{Tags:} one-handed, hilted, bladed 
 
\emph{Speed:} (1n1)$\Rightarrow$(1n2) 
 
\emph{To-Hit:} +STR 
 
\smallskip  \hrule \smallskip \emph{Attacks: }
\begin{itemize}
    \item 1d6 (S) $\triangleright\mkern-7mu\triangleright\mkern-7mu\blacktriangleright$

\end{itemize} 
 
\smallskip  \hrule \smallskip \textit{A simple tool for cutting down brush.} 
 
\vfill
        weapon, basic \hfill Enc: 1 
        }%
\card{89mm}{64mm}{\textbf{\large{Greatsword}} 
 
\emph{Tags:} hilted, two-handed, bladed 
 
\emph{Requirements:} 1 AGI, 2 STR 
 
\emph{Speed:} (1n2) 
 
\emph{To-Hit:} +AGI +STR 
 
\smallskip  \hrule \smallskip \emph{Attacks: }
\begin{itemize}
    \item 2d8 (P) $\blacktriangle$
- 2d10 (S) $\triangleright\mkern-7mu\blacktriangleright\mkern-7mu\triangleright$

\end{itemize} 
 
\smallskip  \hrule \smallskip Robust Edge: increase low rolls required to lose [sharpened] buff by 2 
 
\vfill
        weapon, basic \hfill Enc: 1 
        }%
\card{89mm}{64mm}{\textbf{\large{Mace}} 
 
\emph{Tags:} shafted, one-handed 
 
\emph{Requirements:} 1 STR 
 
\emph{Speed:} (1n2) 
 
\emph{To-Hit:} +STR 
 
\smallskip  \hrule \smallskip \emph{Attacks: }
\begin{itemize}
    \item 1d8 + STR (B) $\triangleright\mkern-7mu\triangleright\mkern-7mu\blacktriangleright$

\end{itemize} 
 
\smallskip  \hrule \smallskip Ignore 3 armor 
 
\vfill
        weapon, basic \hfill Enc: 1 
        }%
\newline%
\newpage%
\card{89mm}{64mm}{\textbf{\large{Club}} 
 
\emph{Tags:} hilted, one-handed 
 
\emph{Speed:} (2n1) 
 
\emph{To-Hit:} +STR 
 
\smallskip  \hrule \smallskip \emph{Attacks: }
\begin{itemize}
    \item 1d8 (B) $\triangleright\mkern-7mu\blacktriangleright\mkern-7mu\triangleright$

\end{itemize} 
 
\vfill
        weapon, basic \hfill Enc: 1 
        }%
\card{89mm}{64mm}{\textbf{\large{Battleaxe}} 
 
\emph{Tags:} two-handed, shafted, bladed 
 
\emph{Requirements:} 1 STR 
 
\emph{Speed:} (2n1) 
 
\emph{To-Hit:} +STR 
 
\smallskip  \hrule \smallskip \emph{Attacks: }
\begin{itemize}
    \item 1d8 + 2*STR (S) $\triangleright\mkern-7mu\triangleright\mkern-7mu\blacktriangleright$

\end{itemize} 
 
\vfill
        weapon, basic \hfill Enc: 1 
        }%
\card{89mm}{64mm}{\textbf{\large{Putrefying Egg}} 
 
\emph{Tags:} ranged, thrown 
 
\emph{Speed:} (1n1) to throw 
 
\emph{To-Hit:} +PER 
 
\smallskip  \hrule \smallskip \emph{Attacks: }
\begin{itemize}
    \item Range: 10 + 2*STR

\end{itemize} 
 
\smallskip  \hrule \smallskip Brittle, bursts extremely easily. When it bursts, create a 7 hex sphere centered on impact. Inflict 1 poison on present when it bursts, and anything that starts or ends its turn in the cloud. 
 
\smallskip  \hrule \smallskip \textit{A dark form floats in cloudy fluid enveloped by a thin membrane. Like a detached pupil floating blindly in an eye entirely consumed by cataracts. Prolonged contact with the egg causes irritation of the skin, then rashes, lesions, necrosis.} 
 
\vfill
        weapon \hfill Enc: 1/3 
        }%
\newline%
\card{89mm}{64mm}{\textbf{\large{Javelin}} 
 
\emph{Tags:} one-handed, shafted 
 
\emph{Requirements:} 1 AGI 
 
\emph{Speed:} (1n1)$\Rightarrow$(2n1) 
 
\emph{To-Hit:} +AGI 
 
\smallskip  \hrule \smallskip \emph{Attacks: }
\begin{itemize}
    \item 1d6 (P) $\blacktriangle$
- (2n1) To-Hit: PERCEPTION   \newline  1d6 + STR (P) [thrown] [range: 5+STR]

\end{itemize} 
 
\vfill
        weapon, basic \hfill Enc: 1/3 
        }%
\card{89mm}{64mm}{\textbf{\large{Primary of the Night-Heron}} 
 
\emph{Tags:} hilted, two-handed, bladed, reach: 2 spaces 
 
\emph{Requirements:} 1 STR 
 
\emph{Speed:} (1n1)$\Rightarrow$(1n2) 
 
\emph{To-Hit:} +AGI 
 
\smallskip  \hrule \smallskip \emph{Attacks: }
\begin{itemize}
    \item 2d6 (S) $\triangleright\mkern-7mu\blacktriangleright\mkern-7mu\triangleright$

\end{itemize} 
 
\smallskip  \hrule \smallskip Ignore 1 Armor. All sharpening takes 3 times longer. Requires 2 PSYCHIC: Before you attempt an attack you can choose to either move one space when you attack or use your To-Hit as a check against the opponents STR. If you pass the check they are pushed back one space. 
 
\smallskip  \hrule \smallskip \textit{An enormous broad black feather, light, thin, deceptively delicate. The vanes of the feather are razor sharp and harder than steel.} 
 
\vfill
         \hfill Enc: 1 
        }%
\card{89mm}{64mm}{\textbf{\large{Pickaxe}} 
 
\emph{Tags:} two-handed, shafted 
 
\emph{Speed:} (2n1) 
 
\emph{To-Hit:} STR 
 
\smallskip  \hrule \smallskip \emph{Attacks: }
\begin{itemize}
    \item 1d6+STR (P) $\triangleright\mkern-7mu\triangleright\mkern-7mu\blacktriangleright$

\end{itemize} 
 
\vfill
        weapon, basic \hfill Enc: 1 
        }%
\newline%
\card{89mm}{64mm}{\textbf{\large{Cutter Mattock}} 
 
\emph{Tags:} two-handed, shafted, heavy 
 
\emph{Requirements:} 1 STR 
 
\emph{Speed:} (2n1) 
 
\emph{To-Hit:} +STR 
 
\smallskip  \hrule \smallskip \emph{Attacks: }
\begin{itemize}
    \item 1d8 (S) $\triangleright\mkern-7mu\triangleright\mkern-7mu\blacktriangleright$

\end{itemize} 
 
\vfill
        weapon, basic \hfill Enc: 1 
        }%
\card{89mm}{64mm}{\textbf{\large{Cutlass}} 
 
\emph{Tags:} one-handed, hilted, bladed 
 
\emph{Speed:} (1n1)$\Rightarrow$(2n1) 
 
\emph{To-Hit:} +AGI 
 
\smallskip  \hrule \smallskip \emph{Attacks: }
\begin{itemize}
    \item 1d8 (S) $\triangleright\mkern-7mu\triangleright\mkern-7mu\blacktriangleright$
- 1d6 (P) $\blacktriangle$

\end{itemize} 
 
\vfill
        weapon, basic \hfill Enc: 1 
        }%
\card{89mm}{64mm}{\textbf{\large{Radiat Thrall}} 
 
\emph{HP:} 2d12 or 13 
 
\emph{Scores:} 1 STR, 1 CON, 1 PSYCHIC 
 
\emph{Skills:} - Screech (3n1): 1d6 + PSYCHIC (P) reach: 2 spaces. 
 
}%
\newline%
\newpage%
\card{89mm}{64mm}{\textbf{\large{Radiat Priest}} 
 
\emph{HP:} 4d10 or 18 
 
\emph{Scores:} 1 STR, 3 PSYCHIC 
 
\emph{Holds:} radiat\_dagger. Ceremonial robes. 
 
}%
\card{89mm}{64mm}{\textbf{\large{Radiat Crusader}} 
 
\emph{HP:} 5d12 or 32 
 
\emph{Scores:} 3 STR, 2 AGI, 2 CON, 3 PSYCHIC 
 
\emph{Holds:} radiat\_greatsword sometimes. Any large sword. Sometimes a shield. The heaviest armor they would reasonably have in the situation. radiat\_crusader\_armor potentially. 
 
}%
\card{89mm}{64mm}{\textbf{\large{Isopod Peacekeeper}} 
 
\emph{HP:} 3d10 or 16 
 
\emph{Scores:} 1 STR, 2 CON 
 
\emph{Holds:} 2 shell\_buckler, 1 great\_claw, sap. 
 
}%
\newline%
\card{89mm}{64mm}{\textbf{\large{Isopod Trophy Hunter}} 
 
\emph{HP:} 3d12 or 19 
 
\emph{Scores:} 1 STR, 2 CON, 1 STEALTH 
 
\emph{Holds:} hunting\_knife, 1d4 hunting\_net, 1d4 great\_claw, 1d4 shell\_buckler. 
 
}%
\card{89mm}{64mm}{\textbf{\large{Isopod Ambassador}} 
 
\emph{HP:} 2d12 or  13 
 
\emph{Scores:} 1 DEX, 2 PERSUASION, 2 STEALTH 
 
}%
\end{document}