\documentclass{article}%
\usepackage[T1]{fontenc}%
\usepackage[utf8]{inputenc}%
\usepackage{lmodern}%
\usepackage{textcomp}%
\usepackage{lastpage}%
\usepackage{parskip}%
\usepackage{geometry}%
\geometry{margin=.07in}%
\usepackage{fdsymbol}%
%
%
%
\begin{document}%
\normalsize%
\newcommand{\card}[3]{\fbox{\begin{minipage}[t][#1][t]{#2} #3 \end{minipage}}}%
\card{89mm}{64mm}{\textbf{\large{Salt Wretch}} 
 
\emph{HP:} 1d10 or 4 
 
\emph{Scores:} 1 STR 
 
\emph{Skills:} - Claw (2n1): 1d4 (S). Enemies take damage = to their current SALT on the beginning of their turn and lose one SALT when within 1 space of the Wretch. 
 
\emph{Holds:} 1d4-3 pickaxe, 1d4-2 curse\_eye. 
 
\smallskip  \hrule \smallskip \textit{A bent creature, shriviled and distended. Rattling sandpaper breathing and muttering. Eyes shriveled and wasted, or a dull black.} 
 
}%
\card{89mm}{64mm}{\textbf{\large{Crust Punk}} 
 
\emph{HP:} 4d10 or 20 
 
\emph{Scores:} 2 STR, 1 CON, 2 HYLIC 
 
\emph{Holds:} 2d100f of SALT. 
 
}%
\card{89mm}{64mm}{\textbf{\large{Nightlight Chicken}} 
 
\emph{HP:} 1d6 or 3 
 
\emph{Scores:} -1 STR, 1 AGI  
 
\emph{Skills:} - Peck and Scratch, (3n1): 1d4-1 (S) + 1 (P).  
 
}%
\newline%
\card{89mm}{64mm}{\textbf{\large{Starving Harvester}} 
 
\emph{HP:} 2d12 13 
 
\emph{Scores:} 1 STR, 1 AGI, 1 CON, 1 HYLIC 
 
\emph{Holds:} foul\_club, hunting\_knife are both standard. Otherwise, really any sharp knife and any bludgeoning weapon, as likely improvised. Weaker Harvesters will tend to have worse equipment. 1d100f of SALT. 
 
}%
\card{89mm}{64mm}{\textbf{\large{Gluttonous Harvester}} 
 
\emph{HP:} 3d12 19 
 
\emph{Scores:} 2 STR, 2 AGI, 2 CON, 2 HYLIC 
 
\emph{Holds:} crimson\_cudgel, cruel\_razor, potentially foul\_club or hunting\_knife. 2d100f of SALT. 
 
}%
\card{89mm}{64mm}{\textbf{\large{Feasting Harvester}} 
 
\emph{HP:} 5d12 or 32 
 
\emph{Scores:} 2 STR, 2 AGI, 3 CON, 4 HYLIC 
 
\emph{Holds:} weeping\_greatclub, screeching\_sickle, are unique to powerful Harvesters. Harvesters might also use other fine bludgeoning weapons or sharp knives. 1d4-1 hunting\_net. 4d100f of SALT. 
 
}%
\newline%
\card{89mm}{64mm}{\textbf{\large{Gold Eater}} 
 
\emph{HP:} 5d6 or 18 
 
\emph{Scores:} 1d4-1 or 2 STR, -2 AGI and DEX, 0 PERCEPTION 
 
}%
\card{89mm}{64mm}{\textbf{\large{Ibex Duke}} 
 
\emph{HP:} 1d12 or 6  
 
\emph{Scores:} 1 STR, 1 AGI 
 
}%
\card{89mm}{64mm}{\textbf{\large{Ibex King}} 
 
\emph{HP:} 3d12 or 19 
 
\emph{Scores:} 1 STR, 1 AGI 
 
}%
\newline%
\newpage%
\card{89mm}{64mm}{\textbf{\large{Illuminated Wretch}} 
 
\emph{HP:} 1d8 or 4 
 
\emph{Scores:} -1 all core stats, 1 PSYCHIC 
 
}%
\card{89mm}{64mm}{\textbf{\large{Lionhead}} 
 
\emph{HP:} 1d12 or 6 
 
\emph{Scores:} -1 all core stats, 3 PSYCHIC 
 
}%
\card{89mm}{64mm}{\textbf{\large{Ant Scout}} 
 
\emph{HP:} 1d12 or 6 
 
\emph{Scores:} 1 STEALTH 
 
}%
\newline%
\card{89mm}{64mm}{\textbf{\large{Ant Soldier}} 
 
\emph{HP:} 3d10 or 16 
 
\emph{Scores:} 1 STR, 1 AGI, 1 DEX  
 
}%
\card{89mm}{64mm}{\textbf{\large{Ant Demon}} 
 
\emph{HP:} 5d10 or 27 
 
\emph{Scores:} 3 STR, 2 AGI 
 
}%
\card{89mm}{64mm}{\textbf{\large{Tchok}} 
 
\emph{HP:} 3d8+1 or 13 
 
\emph{Scores:} 1 CON 
 
\emph{Skills:} Jibbering (1n1): All checks related to magic made within earshot of a
jibbering Tchok are made with -3. This effect stacks with multiple instances
of jibbering. 
 
\emph{Holds:} Carrying 1d4 daggers, 1d6 short spears. 1d6 clubs. 1d2 blowguns.
More rarely poisons that push back the furthest AP token by 1 slot on hit,
consumed on hit. Even more rarely, daggers that can deliver 3 doses of
poison before reapplication is necessary. 
 
\smallskip  \hrule \smallskip \textit{Slimy, stupid, and inane.} 
 
}%
\newline%
\card{89mm}{64mm}{\textbf{\large{Isopod Peacekeeper}} 
 
\emph{HP:} 3d10 or 16 
 
\emph{Scores:} 1 STR, 2 CON 
 
\emph{Holds:} 2 shell\_buckler, 1 great\_claw, sap. 
 
}%
\card{89mm}{64mm}{\textbf{\large{Isopod Trophy Hunter}} 
 
\emph{HP:} 3d12 or 19 
 
\emph{Scores:} 1 STR, 2 CON, 1 STEALTH 
 
\emph{Holds:} hunting\_knife, 1d4 hunting\_net, 1d4 great\_claw, 1d4 shell\_buckler. 
 
}%
\card{89mm}{64mm}{\textbf{\large{Isopod Ambassador}} 
 
\emph{HP:} 2d12 or  13 
 
\emph{Scores:} 1 DEX, 2 PERSUASION, 2 STEALTH 
 
}%
\newline%
\newpage%
\card{89mm}{64mm}{\textbf{\large{Radiat Thrall}} 
 
\emph{HP:} 2d12 or 13 
 
\emph{Scores:} 1 STR, 1 CON, 1 PSYCHIC 
 
\emph{Skills:} - Screech (3n1): 1d6 + PSYCHIC (P) reach: 2 spaces. 
 
}%
\card{89mm}{64mm}{\textbf{\large{Radiat Priest}} 
 
\emph{HP:} 4d10 or 18 
 
\emph{Scores:} 1 STR, 3 PSYCHIC 
 
\emph{Holds:} radiat\_dagger. Ceremonial robes. 
 
}%
\card{89mm}{64mm}{\textbf{\large{Radiat Crusader}} 
 
\emph{HP:} 5d12 or 32 
 
\emph{Scores:} 3 STR, 2 AGI, 2 CON, 3 PSYCHIC 
 
\emph{Holds:} radiat\_greatsword sometimes. Any large sword. Sometimes a shield. The heaviest armor they would reasonably have in the situation. radiat\_crusader\_armor potentially. 
 
}%
\newline%
\end{document}