\documentclass{article}%
\usepackage[T1]{fontenc}%
\usepackage[utf8]{inputenc}%
\usepackage{lmodern}%
\usepackage{textcomp}%
\usepackage{lastpage}%
\usepackage{parskip}%
\usepackage{geometry}%
\geometry{margin=.07in}%
\usepackage{fdsymbol}%
%
%
%
\begin{document}%
\normalsize%
\newcommand{\card}[3]{\fbox{\begin{minipage}[t][#1][t]{#2} #3 \end{minipage}}}%
\card{89mm}{64mm}{\textbf{\large{The Braggart}} 
 
\smallskip  \hrule \smallskip A cloak with bright silver stitching.  When worn, DC 9 illusion of a full set of plate armor. 
 
}%
\card{89mm}{64mm}{\textbf{\large{Lost}} 
 
\smallskip  \hrule \smallskip Two stone birds that constantly tug towards each other, regardless of distance. 
 
}%
\card{89mm}{64mm}{\textbf{\large{Bandage}} 
 
\smallskip  \hrule \smallskip Spend (3n1). Remove 1 [bleed]. Bandages can be improvised out of any cloth. 
 
\smallskip  \hrule \smallskip \textit{A roll of clean cloth.} 
 
}%
\newline%
\card{89mm}{64mm}{\textbf{\large{Simple Whetstone}} 
 
\smallskip  \hrule \smallskip Apply [sharpened] to a [bladed] weapon, takes 30 minutes to apply. The weapon does +1 damage and ignores 1 armor. [sharpened] is lost when you roll a 1 with a damage die. 
 
\smallskip  \hrule \smallskip \textit{A large flat stone bearing faded inscriptions.} 
 
}%
\card{89mm}{64mm}{\textbf{\large{Troll Salts}} 
 
\smallskip  \hrule \smallskip Remove 1 [exhaustion], after 10 minutes take 2 [exhaustion]. Wake up from unconsciousness not caused by negative health. 
 
\smallskip  \hrule \smallskip \textit{A small earthenware jar filled with a strong-smelling coarse powder, sealed with a waxed ball of plant fiber.} 
 
}%
\card{89mm}{64mm}{\textbf{\large{Stolen Ichor}} 
 
\smallskip  \hrule \smallskip (2n1). Get 4 [heal]. 
 
}%
\newline%
\card{89mm}{64mm}{\textbf{\large{Variigoshlovr Root }} 
 
\smallskip  \hrule \smallskip (1n1). Remove 1 [bleed]. 
 
}%
\card{89mm}{64mm}{\textbf{\large{Glowing Root Bundle}} 
 
\smallskip  \hrule \smallskip (1n1). Instantly gain 4 HP. 
 
}%
\card{89mm}{64mm}{\textbf{\large{Valiikon's Whetstone}} 
 
\smallskip  \hrule \smallskip Takes 30 minutes to apply [sharpened]. Inflict 1 poison on hit. Inflict 1 poison if you do 2 poison in one turn. Rolling minimum damage removes [sharpened]. 
 
}%
\newline%
\newpage%
\card{89mm}{64mm}{\textbf{\large{Vial of Verdant Sap}} 
 
\smallskip  \hrule \smallskip (2n1). Gain 2 [heal]. 
 
}%
\card{89mm}{64mm}{\textbf{\large{Footsoldier's Whetstone}} 
 
\smallskip  \hrule \smallskip Takes 30 minutes to apply [sharpened] to a [bladed] weapon. Ignore 3 armor. Rolling 1 for damage twice removes [sharpened]. 
 
\smallskip  \hrule \smallskip \textit{A fragment of a relief etched into heavy white stone. The relief depicts a phalanx of soldiers in formation bearing partisans against an unseen force. The relief is etched deeply with identical runes in various styles.} 
 
}%
\card{89mm}{64mm}{\textbf{\large{Cannibal Whetstone}} 
 
\smallskip  \hrule \smallskip Takes 2 hours to apply [sharpened] to a [bladed] weapon. Whetstone must be soaked in blood before use. Inflict 1 [bleed] on hit. Gain 1 HP at the beginning of your turn as long as the opponent is bleeding. 
 
\smallskip  \hrule \smallskip \textit{A warm mass of striated stone writhing almost imperceptibly. It bears a closed eye on one side, it emanates a silent screaming call.} 
 
}%
\newline%
\card{89mm}{64mm}{\textbf{\large{Crude Frog Idol}} 
 
\smallskip  \hrule \smallskip (3n1). Must be holding the idol with both hands. Ignore 3 poison damage next turn. 
 
\smallskip  \hrule \smallskip \textit{A small, worn, and stained frog idol on a fraying cord of twine. It's wearing an even smaller straw hat. He seems to be smiling.} 
 
}%
\card{89mm}{64mm}{\textbf{\large{Battle Egg Carton and Bandolier}} 
 
\smallskip  \hrule \smallskip Carton holds 24 Putrefying Eggs. Carton will break if it or the person wearing it takes 12 damage in one turn. 
 
\smallskip  \hrule \smallskip \textit{A wooden case made from solid hardwood with round impressions chipped into it. The inside is padded with soft moss.} 
 
}%
\card{89mm}{64mm}{\textbf{\large{Bag of Salt}} 
 
\smallskip  \hrule \smallskip Worth 1d12*10f. 
 
}%
\newline%
\card{89mm}{64mm}{\textbf{\large{Salorbrious}} 
 
\smallskip  \hrule \smallskip For 6 turns, gain 1 SALT every turn. 
 
\smallskip  \hrule \smallskip \textit{A smooth waxed sphere of pure SALT, it feels heavy in the hand. It's just enough to kill a man.} 
 
}%
\card{89mm}{64mm}{\textbf{\large{Tall Salted Peter}} 
 
\smallskip  \hrule \smallskip Gain 3 SALT. 
 
\smallskip  \hrule \smallskip \textit{A long clay vial filled with salt suspended in a dark brown oil and continuously swirling and glittering .} 
 
}%
\card{89mm}{64mm}{\textbf{\large{Curse Eye}} 
 
\smallskip  \hrule \smallskip When crushed, all characters within 3 spaces gain 1d4 CURSE. 
 
\smallskip  \hrule \smallskip \textit{A brittle dull black sphere with a layer of veins on one side.} 
 
}%
\newline%
\newpage%
\card{89mm}{64mm}{\textbf{\large{Rucksack}} 
 
\smallskip  \hrule \smallskip Max encumbrance: 6 + STR, [encumbered] threshold: 3 + STR. 
 
}%
\card{89mm}{64mm}{\textbf{\large{Sling Bag}} 
 
\smallskip  \hrule \smallskip Can be worn with another bag. Max encumbrance: 3. This bag can be switched from being worn on your front or back for [1n1]. Searching and grabbing something from this bag is [2n1]. 
 
}%
\card{89mm}{64mm}{\textbf{\large{Scout's Bag}} 
 
\smallskip  \hrule \smallskip Max encumbrance: 4 + STR. 
 
}%
\newline%
\card{89mm}{64mm}{\textbf{\large{Frame Bag}} 
 
\smallskip  \hrule \smallskip Max encumbrance: 8+STR. [encumbered] threshold: 2+STR. 
 
}%
\card{89mm}{64mm}{\textbf{\large{Stick Bag}} 
 
\smallskip  \hrule \smallskip Can be carried while wearing another bag. Stick must be held with one hand. Max encumbrance: 2 + STR. 
 
}%
\end{document}